Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-12-04 Ben_Manuscripts/stochastic_transport/Draft.tex
removed test from name

  To come up with an analytical equation describing the passage time distributions, 
  one can frame the problem as a pulse of particles at the pore inlet ($z=0$) that 
  spreads out over time as it approaches $L$.

%  This pulse model effectively describes
%  the time-dependent probability distribution of particles which eventually reaches 
%  $L$. The diffusion equation describing this situation is:
%  \begin{equation}
%  \frac{\partial c}{\partial t} + v\frac{\partial c}{\partial x} = D\frac{\partial^2 c}{\partial x^2}
%  \end{equation}
%  where $v$ is some average velocity describing the location of the center of the
%  distribution and $D$ is a diffusion constant. 
%  One can show that the normalized
%  concentration profile is:
  First, consider a pulse spreading out with a fixed mean. It is well known that the 
  time-dependent probability distribution of particle positions is:
  \begin{equation}
  p(x, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-x^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $x = x - vt$ in order to linearly shift the mean as a
  function of time:
  \begin{equation}
  p(x, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-(x - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the number of the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F = \int_x^\infty p~ dx = erfc\bigg(\frac{x - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  and finally take the derivative to arrive at the first passage time distribution:
  \begin{equation}
  P = -\frac{1}{\sqrt{\pi}}e^{-(x - vt)^2 / (4Dt)}\bigg(-\frac{D(x - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \end{equation}

>>>>

  To come up with an analytical equation describing the passage time distributions, 
  one can frame the problem as a pulse of particles instantaneously released at the 
  pore inlet ($z=0$) which moves at a constant velocity and spreads out as it 
  approaches $L$. This gives results equivalent to if we had released each particle
  individually and then analyzed the positions of the ensemble of trajectories as 
  a function of time.

  First, consider an initial pulse spreading out over time with a fixed mean. We can
  solve for the time-dependent probability density of particle positions by solving 
  the one dimensional diffusion equation:
  \begin{equation}
  \frac{\partial p}{\partial t} = D \frac{\partial^2 p}{\partial z^2}
  \end{equation}
  The appropriate initial and boundary conditions are:
  \begin{equation}
  BC1: t > 0, z = \infty, p = 0
  \end{equation}
  \begin{equation}
  BC2: t > 0, z = 0, \frac{\partial p}{\partial z} = 0
  \end{equation}
  \begin{equation}
  IC: t = 0, c = M\delta(z)
  \end{equation}
  where $M$ is the total number of particles in the system. It has been shown 
  elsewhere that the solution to this equation is:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-z^2}{4Dt}\bigg)
  \end{equation}
  We can make the substitution $z = z - vt$ in order to linearly shift the mean as a
  function of time:
  \begin{equation}
  p(z, t) = \frac{1}{\sqrt{4 \pi D t}}exp\bigg(\frac{-(z - vt)^2}{4Dt}\bigg)
  \end{equation}
  One can track the fraction of particles, $F$, that have crossed the pore 
  boundary by integrating:
  \begin{equation}
  F = \int_L^\infty p~dz = erfc\bigg(\frac{L - vt}{2\sqrt{D t}}\bigg)
  \end{equation}
  where $L$ is the pore length. This represents the cumulative first passage 
  time distribution so we take its derivative in order to arrive at the first
  passage time distribution:
  \begin{equation}
  P = -\frac{1}{\sqrt{\pi}}e^{-(L - vt)^2 / (4Dt)}\bigg(-\frac{D(L - vt)}{4(Dt)^{3/2}} - \frac{v}{2\sqrt{Dt}}\bigg)
  \label{eqn:passage_times}
  \end{equation}
